Complementary analysis

### 2025-07-29 procesamiento/04-prod_prep-supplementary-material.Rmd
main code for reproducibility, simulations are missing

plot_low <- 
fit_low %>% 
ggplot(aes(y =estimate,x=n_low, fill=dclass3res_V, color=dclass3res_V,ymin=conf.low, ymax=conf.high,group=dclass3res_V)) +
  # geom_errorbar(alpha=0.8,size=0.5,linetype="solid",color="black") +
  geom_ribbon(alpha=0.8,size=1,linetype="solid",color="black") +
  geom_line(size=1,color="black") +
  geom_point(size=2,color="black") +
  facet_grid(~factor(dclass3res_V, levels=
                       c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"),
                     c("Working Class","Intermediate Class","Service Class"))) +
  scale_fill_manual(values=c("#323232","#989898","#CCCCCC"))+
  scale_color_manual(values=c("#323232","#989898","#CCCCCC"))+
  scale_x_continuous(
  breaks = c(0, 0.25, 0.5, 0.75, 1),
  labels = c("0", "0.25", "0.50", "0.75", "1"))+
  scale_y_continuous(limits = c(-0.5,0.5))+
  labs(
    # caption = paste0("Note: N (individuals) = ",nobs(digclas1_VW_11),"; N (countries) = ",lme4::ngrps(digclas1_VW_11),". Predictive estimates with 95% confidence intervals"),
       x="Class-profile low",y="Redistributive preferences",,tag = "A") +
  theme(legend.position = "none", legend.title = element_blank())

plot_mid<- 
fit_mid %>% 
ggplot(aes(y =estimate,x=n_middle, fill=dclass3res_V, group=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
  geom_ribbon(alpha=0.8,size=1,linetype="solid",color="black") +
  geom_line(size=1,color="black") +
  geom_point(size=2,color="black") +
  facet_grid(~factor(dclass3res_V, levels=
                       c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"),
                     c("Working Class","Intermediate Class","Service Class"))) +
  scale_fill_manual(values=c("#323232","#989898","#CCCCCC"))+
  scale_color_manual(values=c("#323232","#989898","#CCCCCC"))+
    scale_x_continuous(
  breaks = c(0, 0.25, 0.5, 0.75, 1),
  labels = c("0", "0.25", "0.50", "0.75", "1"))+
  scale_y_continuous(limits = c(-0.5,0.5))+
  labs(
    # caption = paste0("Note: N (individuals) = ",nobs(digclas1_VW_11),"; N (countries) = ",lme4::ngrps(digclas1_VW_11),". Predictive estimates with 95% confidence intervals"),
      x="Class-profile Middle",y="Redistributive preferences",tag = "B") +
  theme(legend.position = "none", legend.title = element_blank())

plot_hig <- 
fit_hig %>% 
ggplot(aes(y =estimate,x=n_high, fill=dclass3res_V, group=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
  geom_ribbon(alpha=0.8,size=1,linetype="solid",color="black") +
  geom_line(size=1,color="black") +
  geom_point(size=2,color="black") +
  facet_grid(~factor(dclass3res_V, levels=
                       c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"),
                     c("Working Class","Intermediate Class","Service Class"))) +
  scale_fill_manual(values=c("#323232","#989898","#CCCCCC"))+
  scale_color_manual(values=c("#323232","#989898","#CCCCCC"))+
  scale_x_continuous(
  breaks = c(0, 0.25, 0.5, 0.75, 1),
  labels = c("0", "0.25", "0.50", "0.75", "1"))+
  scale_y_continuous(limits = c(-0.5,0.5))+
  labs(
    # caption = paste0("Note: N (individuals) = ",nobs(digclas1_VW_11),"; N (countries) = ",lme4::ngrps(digclas1_VW_11),". Predictive estimates with 95% confidence intervals",),
       x="Class-profile High",y="Redistributive preferences",tag = "C") +
  theme(legend.position = "none", legend.title = element_blank())

@@

dfreg$socx<- as.numeric(scale(dfreg$socx))

dfreg$gini_disp <- as.numeric(scale(dfreg$gini_disp))

dfreg$ilo_taxrev <- as.numeric(scale(dfreg$ilo_taxrev))
dfreg$ilo_govspe <- as.numeric(scale(dfreg$ilo_govspe))

dfreg$cpi <- as.numeric(scale(dfreg$cpi))
dfreg$mig_share <- as.numeric(scale(dfreg$mig_share))
dfreg$union_den <- as.numeric(scale(dfreg$union_den))
dfreg$v2x_polyarchy <- as.numeric(scale(dfreg$v2x_polyarchy))
dfreg$unemployment_rate <- as.numeric(scale(dfreg$unemployment_rate))
dfreg$egal <- scale(dfreg$egal)

@@

```{r tableS4, results='asis'}
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
ggplot2::theme_set(ggplot2::theme_bw())
ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))

if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
rm(list=ls())

load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(
  prefineq,redist,
  egal = egal2,
  dclass3res_V,
  # dclass3spo_V,
  homclass3_V_res,dclass6res,
  know_total,
  # socialtrust,
  # Q03pcm,
  # edyears,
  female,
  agenum,
  # partner,
  # religion,
  # union,
  # workst, 
  WEIGHT,
  region,
  "gini_disp"=wid_gini_disp,
  "gini_mkt",
  ilo_taxrev,ilo_govspe,abs_red,
  rel_red,
  d10d1=wid_p90p10,
  wid_p90p50,
  top10=wid_sharetop10,
  rgdpna,
  gdppercapita,
  oecd,
  country2, country, country3,
) %>%
  mutate(logrgdpna = log(rgdpna),
         loggdppercapita=log(gdppercapita)
         ) %>%
  # filter(oecd == "OECD") %>%
  filter(country2 != "SVN") 
dfreg$egal <- as.numeric(scale(dfreg$egal))
dfreg <- na.omit(dfreg)

@@

## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$ 
digclas1_VW_0<- lmer(egal~1 + homclass3_V_res + (1|country2),data=dfreg,weights = WEIGHT)
digclas1_VW_1<- lmer(egal~1 + homclass3_V_res+know_total +female+agenum+(1|country2),data=dfreg,weights = WEIGHT)
# digclas1_VW_2<- update(digclas1_VW_1, . ~ . +know_total) 
digclas1_VW_3 <- update(digclas1_VW_1, . ~ . + dclass6res)
# digclas1_VW_5 <- update(digclas1_VW_3, . ~ . + edyears+ Q03pcm+workst)

digclas1_VW_7 <- update(digclas1_VW_3, . ~ . +dclass6res*homclass3_V_res)

digclas1_VW_8 <- update(digclas1_VW_3, . ~ . +dclass6res*homclass3_V_res*gini_disp)

@@

```{r tableS5}
# Main cross-level interaction for Income Inequality---------------------------
int_xlvl_gini <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass6res+
         female_gc+agenum_gc+
         # partner_gc+
         # edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+         
         # workst_gc+
         homclass3_V_gc*
         dclass6res*
         gini_disp + 
         (homclass3_V_gc+dclass6res|country2),data=dfreg,weights = WEIGHT)
# Main cross-level interaction with Welfare State Size--------------------------
int_xlvl_wstate <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass6res+
         female_gc+agenum_gc+
         # partner_gc+
         # edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+         
         # workst_gc+
         gini_disp +
         homclass3_V_gc*
         dclass6res*
         wstate2 + 
         (homclass3_V_gc+dclass6res|country2),data=dfreg,weights = WEIGHT)

# Double cross-level interaction Gini and Welfare State Size (Tax Reveneu)-------
int_xlvl_gini_taxrev <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass6res+
         female_gc+agenum_gc+
         # partner_gc+
         # edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+         
         # workst_gc+
         homclass3_V_gc*dclass6res*gini_disp + 
         homclass3_V_gc*dclass6res*ilo_taxrev + 
         (homclass3_V_gc+dclass6res|country2),data=dfreg,weights = WEIGHT)

# Double cross-level interaction Gini and Welfare State Size (Goverment Spending)------
int_xlvl_gini_govspe <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass6res+
         female_gc+agenum_gc+
         # partner_gc+
         # edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+         
         # workst_gc+
         homclass3_V_gc*dclass6res*gini_disp + 
         homclass3_V_gc*dclass6res*ilo_govspe + 
         (homclass3_V_gc+dclass6res|country2),data=dfreg,weights = WEIGHT)
# Double cross-level interaction Gini and Welfare State Size (Redistribution)----
int_xlvl_gini_redist <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass6res+
         female_gc+agenum_gc+
         # partner_gc+
         # edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+         
         # workst_gc+
         homclass3_V_gc*dclass6res*gini_disp + 
         homclass3_V_gc*dclass6res*abs_red + 
         (homclass3_V_gc+dclass6res|country2),data=dfreg,weights = WEIGHT)

# Double cross-level interaction Gini and Welfare State Size (Index)------------
int_xlvl_gini_wstate <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass6res+
         female_gc+agenum_gc+
         # partner_gc+
         # edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+         
         # workst_gc+
         homclass3_V_gc*dclass6res*gini_disp + 
         homclass3_V_gc*dclass6res*wstate2 + 
         (homclass3_V_gc+dclass6res|country2),data=dfreg,weights = WEIGHT)

# Double cross-level interaction Gini and GDP ----------------------------------
int_xlvl_gini_gdp<- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass6res+
         female_gc+agenum_gc+
         # partner_gc+
         # edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+         
         # workst_gc+
         homclass3_V_gc*dclass6res*gini_disp + 
         homclass3_V_gc*dclass6res*loggdppercapita +
         (homclass3_V_gc+dclass6res|country2),data=dfreg,weights = WEIGHT)

>>>>

plot_low <- 
fit_low %>% 
ggplot(aes(y =estimate,x=n_low, fill=dclass3res_V, color=dclass3res_V,ymin=conf.low, ymax=conf.high,group=dclass3res_V)) +
  # geom_errorbar(alpha=0.8,size=0.5,linetype="solid",color="black") +
  geom_ribbon(alpha=0.8,size=1,linetype="solid",color="black") +
  geom_line(size=1,color="black") +
  geom_point(size=2,color="black") +
  facet_grid(~factor(dclass3res_V, levels=
                       c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"),
                     c("Working Class","Intermediate Class","Service Class"))) +
  scale_fill_manual(values=c("#323232","#989898","#CCCCCC"))+
  scale_color_manual(values=c("#323232","#989898","#CCCCCC"))+
  scale_x_continuous(
  breaks = c(0, 0.25, 0.5, 0.75, 1),
  labels = c("0", "0.25", "0.50", "0.75", "1"))+
  scale_y_continuous(limits = c(-0.5,0.5))+
  labs(
    # caption = paste0("Note: N (individuals) = ",nobs(digclas1_VW_11),"; N (countries) = ",lme4::ngrps(digclas1_VW_11),". Predictive estimates with 95% confidence intervals"),
       x="Ties to Working Class",y="Redistributive preferences",,tag = "A") +
  theme(legend.position = "none", legend.title = element_blank())
plot_mid<- 
fit_mid %>% 
ggplot(aes(y =estimate,x=n_middle, fill=dclass3res_V, group=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
  geom_ribbon(alpha=0.8,size=1,linetype="solid",color="black") +
  geom_line(size=1,color="black") +
  geom_point(size=2,color="black") +
  facet_grid(~factor(dclass3res_V, levels=
                       c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"),
                     c("Working Class","Intermediate Class","Service Class"))) +
  scale_fill_manual(values=c("#323232","#989898","#CCCCCC"))+
  scale_color_manual(values=c("#323232","#989898","#CCCCCC"))+
    scale_x_continuous(
  breaks = c(0, 0.25, 0.5, 0.75, 1),
  labels = c("0", "0.25", "0.50", "0.75", "1"))+
  scale_y_continuous(limits = c(-0.5,0.5))+
  labs(
    # caption = paste0("Note: N (individuals) = ",nobs(digclas1_VW_11),"; N (countries) = ",lme4::ngrps(digclas1_VW_11),". Predictive estimates with 95% confidence intervals"),
      x="Ties to Intermediate Class",y="Redistributive preferences",tag = "B") +
  theme(legend.position = "none", legend.title = element_blank())

plot_hig <- 
fit_hig %>% 
ggplot(aes(y =estimate,x=n_high, fill=dclass3res_V, group=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
  geom_ribbon(alpha=0.8,size=1,linetype="solid",color="black") +
  geom_line(size=1,color="black") +
  geom_point(size=2,color="black") +
  facet_grid(~factor(dclass3res_V, levels=
                       c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"),
                     c("Working Class","Intermediate Class","Service Class"))) +
  scale_fill_manual(values=c("#323232","#989898","#CCCCCC"))+
  scale_color_manual(values=c("#323232","#989898","#CCCCCC"))+
  scale_x_continuous(
  breaks = c(0, 0.25, 0.5, 0.75, 1),
  labels = c("0", "0.25", "0.50", "0.75", "1"))+
  scale_y_continuous(limits = c(-0.5,0.5))+
  labs(
    # caption = paste0("Note: N (individuals) = ",nobs(digclas1_VW_11),"; N (countries) = ",lme4::ngrps(digclas1_VW_11),". Predictive estimates with 95% confidence intervals",),
       x="Ties to Service Class",y="Redistributive preferences",tag = "C") +
  theme(legend.position = "none", legend.title = element_blank())

@@

dfreg$socx<- as.numeric(scale(dfreg$socx))
dfreg$gini_disp <- as.numeric(scale(dfreg$gini_disp))
dfreg$ilo_taxrev <- as.numeric(scale(dfreg$ilo_taxrev))
dfreg$ilo_govspe <- as.numeric(scale(dfreg$ilo_govspe))
dfreg$cpi <- as.numeric(scale(dfreg$cpi))
dfreg$mig_share <- as.numeric(scale(dfreg$mig_share))
dfreg$union_den <- as.numeric(scale(dfreg$union_den))
dfreg$v2x_polyarchy <- as.numeric(scale(dfreg$v2x_polyarchy))
dfreg$unemployment_rate <- as.numeric(scale(dfreg$unemployment_rate))
dfreg$egal <- scale(dfreg$egal)

@@

```{r tableS4, results='asis'}
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
ggplot2::theme_set(ggplot2::theme_bw())
ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg,MLMusingR,lme4)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(
  prefineq,redist,
  egal = egal2,
  dclass3res_V,
  # dclass3spo_V,
  homclass3_V_res,dclass6res,
  know_total,
  # socialtrust,
  # Q03pcm,
  # edyears,
  female,
  agenum,
  # partner,
  # religion,
  # union,
  # workst, 
  WEIGHT,
  region,
  "gini_disp"=wid_gini_disp,
  "gini_mkt",
  ilo_taxrev,ilo_govspe,abs_red,
  rel_red,
  d10d1=wid_p90p10,
  wid_p90p50,
  top10=wid_sharetop10,
  rgdpna,
  gdppercapita,
  oecd,
  country2, country, country3,
) %>%
  mutate(logrgdpna = log(rgdpna),
         loggdppercapita=log(gdppercapita)
         ) %>%
  filter(country2 != "SVN") 
dfreg$egal <- as.numeric(scale(dfreg$egal))
dfreg <- na.omit(dfreg)

@@

## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$ 
digclas1_VW_0<- lmer(egal~1 + homclass3_V_res + (1|country2),data=dfreg,weights = WEIGHT)
digclas1_VW_1<- lmer(egal~1 + homclass3_V_res+know_total +female+agenum+(1|country2),data=dfreg,weights = WEIGHT)
digclas1_VW_3 <- update(digclas1_VW_1, . ~ . + dclass6res)
digclas1_VW_7 <- update(digclas1_VW_3, . ~ . +dclass6res*homclass3_V_res)
digclas1_VW_8 <- update(digclas1_VW_3, . ~ . +dclass6res*homclass3_V_res*gini_disp)

@@

```{r tableS5}
# Main cross-level interaction for Income Inequality---------------------------
int_xlvl_gini <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass6res+
         female_gc+agenum_gc+
         homclass3_V_gc*
         dclass6res*
         gini_disp + 
         (homclass3_V_gc+dclass6res|country2),data=dfreg,weights = WEIGHT)
# Main cross-level interaction with Welfare State Size--------------------------
int_xlvl_wstate <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass6res+
         female_gc+agenum_gc+
         gini_disp +
         homclass3_V_gc*
         dclass6res*
         wstate2 + 
         (homclass3_V_gc+dclass6res|country2),data=dfreg,weights = WEIGHT)

# Double cross-level interaction Gini and Welfare State Size (Tax Reveneu)-------
int_xlvl_gini_taxrev <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass6res+
         female_gc+agenum_gc+
         homclass3_V_gc*dclass6res*gini_disp + 
         homclass3_V_gc*dclass6res*ilo_taxrev + 
         (homclass3_V_gc+dclass6res|country2),data=dfreg,weights = WEIGHT)

# Double cross-level interaction Gini and Welfare State Size (Goverment Spending)------
int_xlvl_gini_govspe <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass6res+
         female_gc+agenum_gc+
         homclass3_V_gc*dclass6res*gini_disp + 
         homclass3_V_gc*dclass6res*ilo_govspe + 
         (homclass3_V_gc+dclass6res|country2),data=dfreg,weights = WEIGHT)
# Double cross-level interaction Gini and Welfare State Size (Redistribution)----
int_xlvl_gini_redist <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass6res+
         female_gc+agenum_gc+
         homclass3_V_gc*dclass6res*gini_disp + 
         homclass3_V_gc*dclass6res*abs_red + 
         (homclass3_V_gc+dclass6res|country2),data=dfreg,weights = WEIGHT)

# Double cross-level interaction Gini and Welfare State Size (Index)------------
int_xlvl_gini_wstate <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass6res+
         female_gc+agenum_gc+
         homclass3_V_gc*dclass6res*gini_disp + 
         homclass3_V_gc*dclass6res*wstate2 + 
         (homclass3_V_gc+dclass6res|country2),data=dfreg,weights = WEIGHT)

# Double cross-level interaction Gini and GDP ----------------------------------
int_xlvl_gini_gdp<- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass6res+
         female_gc+agenum_gc+
         homclass3_V_gc*dclass6res*gini_disp + 
         homclass3_V_gc*dclass6res*loggdppercapita +
         (homclass3_V_gc+dclass6res|country2),data=dfreg,weights = WEIGHT)
